### 2024-03-10 chapter_3/src/chapter_3.qmd
adding a couple more descriptives

# Load the data
df_descriptives <- dbGetQuery(
  con,
  "
  SELECT
    Age,
    Gender AS 'Gender (Male, Female, Non-Binary, Other)',
    Education,
    White,
    Attention,
    Dem3 AS 'PID (Republican, Independent, Democrat)',
    DislikeArgue AS 'Dislike Arguing',
    EnjoyChallenge AS 'Enjoy Challenging'
  FROM 
    Clean;
  "
)
df_primed <- dbGetQuery(con, "SELECT * FROM Clean WHERE CorrectColor=1 AND PoliticalPrime == 1;")
```

@@

To address $H_1$, the outcome variable of interest is whether or not people notice the color of the shirt (0 or 1,) as explained by whether they received the political prime or not (0 or 1). To measure whether participants notice the color of the shirt, I ask them to report what the color of the shirt was. I then compare that to the color of the shirt that they actually saw. Those who reported the correct color received a value of 1 and those who were incorrect received a value of 1. I fit a logistic regression to examine whether there are differences in the outcome depending on this prime.

>>>>

# Load the data
df_descriptives <- dbGetQuery(
  con,
  "
  SELECT
    Age,
    Gender AS 'Gender (Male, Female, Non-Binary, Other)',
    Education,
    White,
    Attention,
    Dem3 AS 'PID (Republican, Independent, Democrat)',
    DislikeArgue AS 'Dislike Arguing',
    EnjoyChallenge AS 'Enjoy Challenging'
  FROM 
    Clean;
  "
)
df_h1 <- dbGetQuery(con, "SELECT CorrectColor FROM Clean")
df_primed <- dbGetQuery(con, "SELECT * FROM Clean WHERE CorrectColor=1 AND PoliticalPrime == 1;")
```

@@

To address $H_1$, the outcome variable of interest is whether or not people notice the color of the shirt (0 or 1,) as explained by whether they received the political prime or not (0 or 1). To measure whether participants notice the color of the shirt, I ask them to report what the color of the shirt was. I then compare that to the color of the shirt that they actually saw. Those who reported the correct color received a value of 1 and those who were incorrect received a value of 1. @tbl-h1-descriptive presents the descriptive statistics for the sample.

```{r}
#| label: tbl-h1-descriptive
#| tbl-cap: Sample performance of noticing color
#| echo: false
datasummary_skim(data=df_h1)
```

I fit a logistic regression to examine whether there are differences in the outcome depending on this prime.
